A new method to estimate dark matter halo concentrations

### 2015-01-24 paper/article.tex
quitando notas viejas
solved issue

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure*}
\begin{center}
  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
\end{center}
\caption{Comparison between the obtained concentrations by the three methods
    \label{fig:mdv}}
\end{figure*}

@@

\verb"http://adsabs.harvard.edu/abs/2014ApJ...795..163U"
\verb"http://adsabs.harvard.edu/abs/2012ApJS..199...25P" Figura 3!
\end{document}

>>>>

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by our method and the velocity method
  \label{fig:mdv}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by our method and the density method
  \label{fig:mdv}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by the density method and the velocity method
  \label{fig:mdv}}
\end{figure}

@@

\end{document}
